Model Search in Relational Domains

### 2016-10-22 algorithm.tex
fixes in sec4

\Output{The status \safe or \unsafe.}

@@

  \return (\unsafe)}

@@

abstract transformers $\abstransset$ w.r.t.\ an abstract domain~$\domain$. \pscmt{define} 
The algorithm is parametrised by propagation $(\propheur)$, decision
$(\decheur)$, and conflict analysis heuristics $(\confheur)$.  

@@

trail $\trail$.  The decision $\decisionvar$ therefore refines \rmcmt{not
defined} the current abstract value $\abs(\trail)$ represented by the trail. 
%\rmcmt{a decision is added to the trail only if it refines the trail.}

>>>>

\Output{The status \safe or \unsafe. %and a counterexample if \unsafe.

@@

  \return \unsafe}

@@

abstract transformers
$\abstransset=\{\abstrans{\domain}{\sigma}|\sigma\in\Sigma\}$
w.r.t.\ an abstract domain~$\domain$.  The algorithm is parametrised
by propagation $(\propheur)$, decision $(\decheur)$, and conflict
analysis heuristics $(\confheur)$.

@@

trail $\trail$.  The decision $\decisionvar$ refines  the current abstract value $\abs(\trail)$ represented by the trail, i.e.\ $\abs(\trail\cdot\decisionvar)\sqsubseteq \abs(\trail)$.
